Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-08-27 doc/paper.Rmd
fix table

```{r label="results-table"}
flextable(results_df) %>% 
  merge_v(j = c(2)) %>% 
  valign(j = c(2), valign = "top") %>% 
  align(j = c(5, 7), align = "right", part = "all") %>%
  colformat_double(j = c(3,6), digits = 2) %>% 
  fix_border_issues() %>% 
  flextable::compose(j = 3, part = "header",
                     value = as_paragraph("R", as_sup("2"))) %>% 
  flextable::compose(j = 4, i = c(4,9,15,20,26,31),
                     value = as_paragraph("s(log(size", as_sub("t"), "))")) %>%
  flextable::compose(j = 1, i = 12, 
                     value = as_paragraph("log(size", as_sub("t+1"), ")")) %>% 
  autofit() %>% 
  set_caption(result_cap, style = "Image Caption")
```

>>>>

```{r label="results-table"}
flextable(results_df) %>% 
  merge_v(j = c(1,2,3)) %>% 
  valign(j = c(1,2,3), valign = "top") %>% 
  align(j = c(5, 7), align = "right", part = "all") %>%
  colformat_double(j = c(3,6), digits = 2) %>% 
  fix_border_issues() %>% 
  flextable::compose(j = 3, part = "header",
                     value = as_paragraph("model R", as_sup("2"))) %>% 
  flextable::compose(j = 4, i = c(2,6,10,14,18,22),
                     value = as_paragraph("s(log(size", as_sub("t"), "))")) %>%
  flextable::compose(j = 1, i = 9, 
                     value = as_paragraph("log(size", as_sub("t+1"), ")")) %>% 
  autofit() %>% 
  set_caption(result_cap, style = "Image Caption")
```
